Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-29 tab-hmeff.tex
tex

}

\caption{Effectiveness of Hardness Manipulation for Adversarial Training.}
\label{tab:hmeff}
\end{table*}

>>>>

} \vspace{-0.5em}
	%
\caption{Effectiveness of Hardness Manipulation for Adversarial Training.
%
The ``$\uparrow$'' mark means ``the higher the better'', while ``$\downarrow$''
	means the opposite.
%
ACT[$\mathcal{R}$] and ACT[$\mathcal{S}$] mean the training triplet is sampled
	using Random and Softhard strategy, respectively.
%
	}
	%
\label{tab:hmeff}
%
\end{table*}
